A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-27 sections/Metatheory.tex
S4.3-4.4 corollaries

\begin{corollary}[Soundness, single judgment form]
Given \emph{wf }$\Psi$ and $\Gm = \Psi$:
\begin{enumerate}
    \item If $\Gm \Vdash A \le B \redto \nil$ then $\Psi \vdash A \le B$;
    \item If $\Gm \Vdash e \Lto A \redto \nil$ then $\Psi \vdash e \Lto A$;
    \item If $\Gm \Vdash e \To_a \jg \redto \nil$ for any $\jg$, then there exists $A$
        s.t. $\Psi \vdash e \To A$;
    \item If $\Gm \Vdash \appInfAlg{A}{e} \redto \nil$ for any $\jg$, then there exists $C$
        s.t. $\Psi \vdash \appInf{A}{e}{C}$.
\end{enumerate}
\end{corollary}
\bruno{I do not think the corollary is precisely stated. I think you want todo
  instantiation on $\Gm$ and then use erasure on the judgements, right? As it stands
  it is wrong because there is a ``type error''. Worklists and declarative typing contexts are of different shapes
so the equality does not make sense.}

@@

\begin{lemma}[Prune Transfer for Instantiation]
If $(\Gm \Vdash \al \le A \to B) \sto (\Om \Vdash C \le A_1 \to B_1)$ and
$\Om \vdash C \le A_1 \to B_1$, then $\al\notin FV(A) \cup FV(B)$.
\end{lemma}

The following corollary is derived immediately from Theorem~\ref{thm:completeness}.
\begin{corollary}[Completeness, single judgment form]
Given \emph{wf }$\Psi$ and $\Gm = \Psi$:
\begin{enumerate}
    \item If $\Psi \vdash A \le B$ then $\Gm \Vdash A \le B \redto \nil$;
    \item If $\Psi \vdash e \Lto A$ then $\Gm \Vdash e \Lto A \redto \nil$;
    \item If $\Psi \vdash e \To A$ then $\Gm \Vdash e \To_a 1 \le 1 \redto \nil$;
    \item If $\Psi \vdash \appInf{A}{e}{C}$ then $\Gm \Vdash \appInfAlg{A}{e}[a][1 \le 1] \redto \nil$.
\end{enumerate}
\end{corollary}
\bruno{Similar problem to the soundness corollaries here.}

>>>>

\begin{corollary}[Soundness, single judgment form]
Given \emph{wf }$\Gm$:
\begin{enumerate}
    \item If $\Gm \Vdash A \le B \redto \nil$\\
        then there exist $A', B', \Om$ s.t.
        $\Gm \Vdash A \le B \sto \Om \Vdash A' \le B'$ and $\|\Om\| \vdash A' \le B'$;
    \item If $\Gm \Vdash e \Lto A \redto \nil$\\
        then there exist $e', A', \Om$ s.t.
        $\Gm \Vdash e \Lto A \sto \Om \Vdash e \Lto A'$ and $\|\Om\| \vdash e \Lto A'$;
    \item If $\Gm \Vdash e \To_a \jg \redto \nil$ for any $\jg$\\
        then there exists $\Om, \jg', A$ s.t.
        $\Gm \sto \Om$ and $\|\Om\| \vdash e \To A$;
    \item If $\Gm \Vdash \appInfAlg{A}{e} \redto \nil$ for any $\jg$\\
        then there exists $\Om, \jg', A', C$ s.t.
        $\Gm \Vdash \appInfAlg{A}{e} \sto \Om \Vdash \appInfAlg{A'}{e}[a][\jg']$
            and $\|\Om\| \vdash \appInf{A'}{e}{C}$.
\end{enumerate}
\end{corollary}
\bruno{I do not think the corollary is precisely stated. I think you want todo
  instantiation on $\Gm$ and then use erasure on the judgements, right? As it stands
  it is wrong because there is a ``type error''. Worklists and declarative typing contexts are of different shapes
so the equality does not make sense.}

@@

\begin{lemma}[Prune Transfer for Instantiation]
If $(\Gm \Vdash \al \le A \to B) \sto (\Om \Vdash C \le A_1 \to B_1)$ and
$\|\Om\| \vdash C \le A_1 \to B_1$, then $\al\notin FV(A) \cup FV(B)$.
\end{lemma}

The following corollary is derived immediately from Theorem~\ref{thm:completeness}.
\begin{corollary}[Completeness, single judgment form]
Given \emph{wf }$\Gm$ containing no judgment chains:
\begin{enumerate}
    \item If $\Gm \Vdash A \le B \sto \Om \Vdash A' \le B'$ and $\|\Om\| \vdash A' \le B'$
        then $\Gm \Vdash A \le B \redto \nil$;
    \item If $\Gm \Vdash e \Lto A \sto \Om \Vdash e \Lto A'$ and $\|\Om\| \vdash e \Lto A'$
        then $\Gm \Vdash e \Lto A \redto \nil$;
    \item If $\Gm \sto \Om$ and exists $A$ s.t. $\|\Om\| \vdash e \To A$
        then $\Gm \Vdash e \To_a 1 \le 1 \redto \nil$;
    \item If $\Gm \Vdash \appInfAlg{A}{e}[a][1 \to 1] \sto \Om \Vdash \appInfAlg{A'}{e}[a][1 \to 1]$
        and exists $C$ s.t. $\|\Om\| \vdash \appInf{A'}{e}{C}$
        \\
        then $\Gm \Vdash \appInfAlg{A}{e}[a][1 \le 1] \redto \nil$.
\end{enumerate}
\end{corollary}
\bruno{Similar problem to the soundness corollaries here.}
